### 2019-07-29 thesis.tex
*** empty log message ***

\chapter{Applications to astrophysical plasmas}
\label{appD}
% On Earth, the plasma is considered an exotic state of matter, associated to the
% glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
% laboratories, and the promise of cleaner and practically inexhaustible energy
% source once we have controlled and energetically efficient thermonuclear fusion
% \cite{bell}. Naturally occurring plasmas in our everyday life are rare, restricted
% to the occurrence of lightning during storms, flames, and the beautiful auroras
% that take place at high latitudes. In the space, however, the situation is the
% opposite. Starting in the outer layers of Earth's atmosphere, passing through the
% solar wind in the interplanetary space, to the stellar interiors and atmospheres,
% accretion disks, and molecular clouds it is estimated that something around
% $99 \sim 99.9\%$ of the observable matter in the universe is in the plasma state
% \cite{may}. Therefore, the study of the physics of plasma processes is a
% fundamental branch of astrophysics\cite{tsypa}.

The analysis presented in this doctoral thesis has relevant contributions in the
study of the combined action of nonlinear kinetic instabilities and collisional
processes in unmagnetized, fully ionized, hydrogen plasmas. Though the plasma's
profile under consideration might be considered quite idealized, the physical
processes that are being addressed have fundamental character - the plasma waves
under consideration and the particle interactions are inherent to any plasma.
The underlying nature of these processes means that they might impact the plasma
dynamics at different astrophysical environments and also in laboratory plasmas.
Laboratory plasmas, however, are usually constrained by very specific conditions
that are unique to each experiment. This specificity makes the analysis in the
experimental context counter productive. A more broad approach was then to compare
our theoretical results with phenomena observed in the naturally occurring space
plasma\footnote{In the literature, the term ``astrophysical plasma'' is sometimes
  used to refer to the plasma observed outside the solar system, while ``space
  plasma'' is used to account for the plasma in our interplanetary space. In this
  text, however, both terms are being used as synonyms.}. The accessibility to
direct, in situ measurements, highly resolved remote sensing and high-resolution
spectroscopy make of the solar plasma the right choice for our analysis.

% In order to offer a deeper insight on the solar phenomena 
% In this appendix, we make a brief description of the solar processes that are
% being addressed by our theory.

\section{}
\label{sec:solar-physics}
The Sun is a G2 main-sequence star. From the stellar astrophysics point
of view, it is considered ordinary, without any unique property that could
differentiate it from other main-sequence stars; except for the fact that
it is remarkably close to us. These two facts make the Sun a perfect model
of study, not only for stellar evolution theorists but also for plasma
physicists.

>>>>

\chapter{Applications to astrophysical plasmas}
\label{appD}
% On Earth, the plasma is considered an exotic state of matter, associated to the
% glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
% laboratories, and the promise of cleaner and practically inexhaustible energy
% source once we have controlled and energetically efficient thermonuclear fusion
% \cite{bell}. Naturally occurring plasmas in our everyday life are rare, restricted
% to the occurrence of lightning during storms, flames, and the beautiful auroras
% that take place at high latitudes. In the space, however, the situation is the
% opposite. Starting in the outer layers of Earth's atmosphere, passing through the
% solar wind in the interplanetary space, to the stellar interiors and atmospheres,
% accretion disks, and molecular clouds it is estimated that something around
% $99 \sim 99.9\%$ of the observable matter in the universe is in the plasma state
% \cite{may}. So understanding the basic physics of plasma processes might help on
% interpreting and describing

The analysis presented in this doctoral thesis has relevant contributions in the
study of the combined action of nonlinear kinetic instabilities and collisional
processes in unmagnetized, fully ionized, hydrogen plasmas. Though the plasma's
profile under consideration might be considered quite idealized, the physical
processes that are being addressed have fundamental character - the plasma waves
under consideration and the particle interactions are inherent to any plasma.
The underlying nature of these processes means that they might impact the plasma
dynamics at different astrophysical environments and also in laboratory plasmas.
Laboratory plasmas, however, are usually constrained by very specific conditions
that are unique to each experiment. This specificity makes the analysis in the
experimental context counter productive. A more broad approach was then to compare
our theoretical results with phenomena observed in the naturally occurring space
plasma\footnote{In the literature, the term ``astrophysical plasma'' is sometimes
  used to refer to the plasma observed outside the solar system, while ``space
  plasma'' is used to account for the plasma in our interplanetary space. In this
  text, however, both terms are being used as synonyms.}.

Astrophysical plasmas are observed in a vast range of densities, temperatures,
magnetic fields, and scale lengths\footnote{For a relatively brief, but
  comprehensive, description of the scales and characteristics of cosmic plasmas,
  see Section 1.2 of Ref. \cite{peratt2014}.}. Starting in the outer layers of
Earth's atmosphere, passing through the solar wind in the interplanetary space,
to the stellar interiors and atmospheres, accretion disks, and molecular clouds
it is estimated that something around $99 \sim 99.9\%$ of the observable matter
in the universe is in the plasma state\cite{may}. Most of these plasmas are quite
far from our measurement instruments, being accessible only through analysis of
the electromagnetic spectrum emitted from their remote location.

% The accessibility to
% direct, in situ measurements, highly resolved remote sensing and high-resolution
% spectroscopy make of the solar plasma the right choice for our analysis.

\section{Solar physics}
\label{sec:solar-physics}

The solar system is permeated with a constant plasma flow of solar origin.
This tenuous and rapid flowing plasma, know as \emph{solar wind}, is
expelled

% The Sun is a G2 main-sequence star. From the stellar astrophysics point
% of view, it is considered ordinary, without any unique property that could
% differentiate it from other main-sequence stars; except for the fact that
% it is remarkably close to us. These two facts make the Sun a perfect model
% of study not only for several areas of astrophysics, like stellar structure
% and evolution, but also for plasma physics.
